Weather covariance matrices as U_hyp for GR50

### 2021-02-10 R/Analysis_v0.6_QTL_interval_plotting.Rmd
Make DOE Poster and Figures

  ggb1 %>%
  ggplot() + 
  geom_point(mapping = aes(x = Garden, y = .data$mn)) +
  switchgrassGWAS::theme_oeco +
  geom_errorbar(mapping = aes(ymin = .data$mn - .data$se,
                              ymax = .data$mn + .data$se,
                              x = Garden), width = 0.3) +
  geom_hline(yintercept = 0, lty = 2) +
  facet_wrap(~Pos_plot+subpop, nrow = 1) +
  labs(x = "", y = "Effect Size (% total variation)") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  coord_flip()

  ave_plot(filename = "../manuscript/plots/Figure_DOE_mash_SNP_effects.png", plot = last_plot(), base_height = 2.4, base_width = 2)
```

>>>>

  ggb1 %>%
  ggplot() + 
  geom_point(mapping = aes(x = Garden, y = .data$mn)) +
  switchgrassGWAS::theme_oeco +
  geom_errorbar(mapping = aes(ymin = .data$mn - .data$se,
                              ymax = .data$mn + .data$se,
                              x = Garden), width = 0.3) +
  geom_hline(yintercept = 0, lty = 2) +
  facet_wrap(~Pos_plot+subpop, nrow = 1) +
  labs(x = "", y = "Effect Size (%)") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  coord_flip()

  save_plot(filename = "../manuscript/plots/Figure_DOE_mash_SNP_effects.png", plot = last_plot(), base_height = 2.4, base_width = 2)
```

### 2021-02-10 R/Analysis_v0.6_weather_covariance_Uhyp_greenup.Rmd
Make DOE Poster and Figures

Chr06N_41610882
mash_plot_effects(m_midw_fl_hyp, i = 41793)
```
Not many SNPs with U_hyp loading > 10% and SNP with log10BF > 2:
Both GR: 10 & 9 SNPs   cgdd_12c_18d_Gulf_and_Midwest x2 (0.9 and 0.10)
Both FL: 2 SNPs        dyln_change_sec_Midwest.7

@@

save_plot(filename = "../manuscript/plots/Figure_3_Data_driven_Covariance_matrices.png", plot = last_plot(), base_height = 10, base_width = 11)
```

>>>>

@@

save_plot(filename = "../manuscript/plots/Figure_3_Data_driven_Covariance_matrices.png", plot = last_plot(), base_height = 10, base_width = 11)

save_plot(filename = "../manuscript/plots/Partial/AP_Flowering_Both.png", plot = f3x, base_height = 2, base_width = 2)
save_plot(filename = "../manuscript/plots/Partial/DS_Flowering_Both.png", plot = f3w, base_height = 2, base_width = 2)

ggdraw() +
  draw_plot(f3w, x = 0, y = 0, width = 0.5, height = 6/7) +
  draw_plot(f3x, x = 0.5, y = 0, width = 0.5, height = 6/7) +
  draw_plot(f3w_leg, x = 0.335, y = 0.725, width = 0.1, height = 0.1) +
  draw_label(label = "Sign changes (AP)", x = 0.2, y = 0.92, size = 10) +
  draw_label(label = "Magnitude changes (DS)", x = 0.73, y = 0.92, size = 10)
save_plot(filename = "../manuscript/plots/Partial/AP_DS_Flowering_Both.png", plot = last_plot(), base_height = 2, base_width = 3.5)
```
